Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-08 paper/paper_new.tex
Tweaking images and such.

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images (e.g.\ low contrast, inadequate lighting,
out-of-focus or cluttered visual arrangements) provide inadequate input
for automated
image analysis and ML algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (\(\frac{\mathrm{pixels}}{\mathrm{cm}}\)) is needed; thus
requiring the ability to identify and measure rulers in the images.
Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
specimen taxon, geographic location, and several other descriptive aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %ML? or okay here
to examine thousands of images
to determine if, for example, a specific fish grows to different lengths
in different habitats, or the temporal evolution of an anatomical feature,
e.g.~the size of a dorsal fin.
\begin{figure*}
  \centering
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100682}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
  \caption{Three example images from the Illinois Natural History Survey (INHS) collection.}
  \label{fig:INHS_examples}
\end{figure*}

Since digital collections may each contain tens of thousands of images, manually producing image-related metadata for each digitized specimen is both labor- and time-intensive and prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in research specimen image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimens.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which is developing a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of ML and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
have been  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
Figure \ref{fig:INHS_examples} presents three typical images used in our
study.
%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results. I guess it's okay to give this in introduction. Just wanted to raise this point. I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both. I think it's okay as I re-read it, but good to have someone check.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results, along with discussion, are presented. The conclusion highlights key findings and identifies next steps.

@@

Iqbal et al.~\cite{Iqbal2021AutomaticFS} used a modified
AlexNet \cite{AlexNet2012} model to classify six different fish species
with 90\% accuracy.

@@

\begin{figure*}[t]
  \centering
 \includegraphics[width=.45\linewidth]{images/teaser1_crop}
  \hspace{5mm}
  \includegraphics[width=.45\linewidth]{images/teaser2_crop}
  \caption{Initial object detection on two specimen images using Detectron2~\cite{wu2019detectron2}.}
  \label{fig:teaser}
\end{figure*}

@@

The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.  Most of these images have been configured, produced and acquired with a standard procedure.  The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.  See Figure \ref{fig:INHS_examples} for three example images from the collection. While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that ML and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.

>>>>

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images (e.g.\ low contrast, inadequate lighting,
out-of-focus or cluttered visual arrangements) provide inadequate input
for automated
image analysis and ML algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (\(\frac{\mathrm{pixels}}{\mathrm{cm}}\)) is needed; thus
requiring the ability to identify and measure rulers in the images.
Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
specimen taxon, geographic location, and several other descriptive aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %ML? or okay here
to examine thousands of images
to determine if, for example, a specific fish grows to different lengths
in different habitats, or the temporal evolution of an anatomical feature,
e.g.~the size of a dorsal fin.
\begin{figure}[t]
  \centering
  % \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
  % \hspace{1mm}
  \includegraphics[width=.95\linewidth]{images/INHS_FISH_100682}
  % \hspace{1mm}
  % \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
  \caption{An image from the Illinois Natural History Survey (INHS) collection.}
  \label{fig:INHS_examples}
\end{figure}

Since digital collections may each contain tens of thousands of images, manually producing image-related metadata for each digitized specimen is both labor- and time-intensive and prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in research specimen image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimens.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which is developing a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of ML and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
have been  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
Figure \ref{fig:INHS_examples} presents a typical image used in our
study.
%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results. I guess it's okay to give this in introduction. Just wanted to raise this point. I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both. I think it's okay as I re-read it, but good to have someone check.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results, along with discussion, are presented. The conclusion highlights key findings and identifies next steps.

@@

Iqbal et al.~\cite{Iqbal2021AutomaticFS} used a
deep learning
% modified AlexNet \cite{AlexNet2012}
model to classify six different fish species with 90\% accuracy.

@@

\begin{figure}[t]
  \centering
 % \includegraphics[width=.45\linewidth]{images/teaser1_crop}
  % \hspace{5mm}
  \includegraphics[width=.95\linewidth]{images/teaser2_crop}
  \caption{Initial object detection on a specimen image using Detectron2~\cite{wu2019detectron2}.}
  \label{fig:teaser}
\end{figure}

@@

The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.  Most of these images have been configured, produced and acquired with a standard procedure.  The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.  See Figure \ref{fig:INHS_examples} for an example image from the collection. While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that ML and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.
